Open Experimental Powder X-ray Diffraction Database

### 2024-04-29 chapters/04_our_dataset.tex
Added todos in introduction

In collaboration with several other institutions we have collected a dataset of diffractograms stemming from experiment, some of them labeled with corresponding structural information. \\
Currently, institutions that contributed towards our dataset include:
\item Institute of Nanotechnology at Karlsruhe institute of technology
\item University of Southern California
\item Lawrence Berkeley National Laboratory

@@

A major advantage of this dataset over other comparable datasets is that is is very easy to handle in python and in PyTorch. \\
Our accompanying python library xrdpattern (https://github.com/aimat-lab/xrdpattern) provides a means to read in as much of the dataset as fits in memory simply by using PatternDB.load(data_dirpath). The patterns attribute of this class is a list of the indivdual pattern diffractograms, each of which supports a standardize, plot and to tensor method. \\
The standardize method returns a "standardized" version of the pattern with a fixed angle range, a fixed number of entries and intensities normalized to the $[0,1]$ interval.

>>>>

In collaboration with several other institutions we have collected a dataset of diffractograms stemming from experiment, some of them labeled with corresponding structural information. \\
Currently, institutions that contributed towards our dataset include:
\begin{itemize}
    \item Institute of Nanotechnology at Karlsruhe institute of technology
    \item University of Southern California
    \item Lawrence Berkeley National Laboratory
\end{itemize}

@@

A major advantage of this dataset over other comparable datasets is that is is very easy to handle in python and in PyTorch.
Our accompanying python library xrdpattern (https://github.com/aimat-lab/xrdpattern) provides a means to read in as much of the dataset as fits in memory simply by using PatternDB.load(data\_dirpath). The patterns attribute of this class is a list of the indivdual pattern diffractograms, each of which supports a standardize, plot and to tensor method. \\
The standardize method returns a "standardized" version of the pattern with a fixed angle range, a fixed number of entries and intensities normalized to the $[0,1]$ interval.
